Analysis paper

### 2021-06-24 analysis/analysis.Rmd
update plots and tables

  scores <- scores[, lapply(.SD, FUN = function(x) {
    if (is.numeric(x)) {
      return(round(signif(x, 3), 2))
    } else {
      return(x)
    }
  })]

@@

>>>>

@@

  # round digits
  df <- df[, lapply(.SD, FUN = function(x) {
    if (is.numeric(x)) {
      return(round(signif(x, 3), 2))
    } else {
      return(x)
    }
  })]

  percentage_cols <- c("interval_score", "interval_score_0.5", 
                       "interval_score_sd", "sharpness", "underprediction", 
                       "overprediction", "aem")

  # no idea how to do that in data.table: 
  df <- df %>%
    dplyr::group_by(horizon, target_type) %>%
    dplyr::mutate_at(percentage_cols, ~ paste0(., " (", 
                                               round(100 * ./.[model == "Hub-ensemble"]), 
                                               "%)"))

  setDT(df)
